---
title: "p8105_hw1_dd2948"
author: "David DeStephano"
date: "September 15, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 0.2
This “problem” focuses on correct styling for your solutions to Problems 1 and 2. We will look for:

meaningful variable / object names
readable code (one command per line; adequate whitespace and indentation; etc)
clearly-written text to explain code and results
a lack of superfluous code (no unused variables are defined; no extra library calls; ect)

## Problem 1
```{r}
library(tibble)
library(tidyverse)
hw_one_df = tibble(
  random_sample = rnorm(8, sd = 1), 
  vec_logical = random_sample > 0, 
  #check if "True" when greater than 0
  
  vec_char = c("Dave", "Ashley", "Brian", "Luke", "Jackson", "Emma", "Katherine", "Eight"),
  
  vec_factor = factor(c("male", "female", "male", "male", "male", "female", "female", "number" ))
)

mean(pull(hw_one_df, random_sample))
mean(pull(hw_one_df, vec_logical))
mean(pull(hw_one_df, vec_char))
mean(pull(hw_one_df, vec_factor))
```
You can only get the mean of variables that have numeric values, you can not take a mean for variables are character variables eg:names or classes

#Code Chunk 1 CHANGE TO PULL??
```{r}
num_vec_logical <- as.numeric(hw_one_df$vec_logical)
num_vec_char <- as.numeric(hw_one_df$vec_char)
num_vec_factor <- as.numeric(hw_one_df$vec_factor)
```

#Code Chunk 2  CHANGE TO PULL?? and naming??
```{r}
#convert the logical vector to numeric, and multiply the random sample by the result
num_vec_logical2 <- as.numeric(hw_one_df$vec_logical)
num_vec_logical2*hw_one_df$random_sample

#convert the logical vector to a factor, and multiply the random sample by the result
num_vec_logical3 <- as.factor(hw_one_df$vec_logical)
num_vec_logical3*hw_one_df$random_sample
#NOT MEANINGFUL FOR FACTORS

#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
num_vec_logical4 <- as.factor(hw_one_df$vec_logical)
num_vec_logical4 <- as.numeric(num_vec_logical4)
num_vec_logical4*hw_one_df$random_sample

```
##Problem 2
Create a data frame comprised of:
x: a random sample of size 500 from a standard Normal distribution
y: a random sample of size 500 from a standard Normal distribution
A logical vector indicating whether x + y > 1
A numeric vector created by coercing the above logical vector
A factor vector created by coercing the above logical vector

```{r}
hw_one_df = tibble(
  x = rnorm(500, sd = 1),
  y = rnorm(500, sd = 1), 
  q2_vec_logical = x + y > 0,
  q2_vec_num = as.numeric(q2_vec_logical),
  q2_vec_factor = as.factor(q2_vec_logical)
)
```  
  
  






```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
